Dual selection games

### 2018-07-17 articles/dual-selection-games/article.tex
start revising to use coinitial reflections

\begin{abstract}
  Often, selection games have dual games for which a winning
  strategy for a player in one game may be used to create
  a winning strategy 
  For example, the Rothberger selection game involving open covers
  is dual to the point-open game. This extends to a general
  theorem: if \(\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\)
  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
  collects the choice functions on the set \(\mc R\),
  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
  are dual selection games. 
\end{abstract}

@@

\begin{definition}
  The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\mc A= \{\ran f:f\in\mathbf C(\mc R)\}.\]
\end{definition}

@@

\begin{proposition}
  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
\end{proposition}
\begin{proof}
  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).

  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
  showing \(x\in\bigcup\mc A\).
\end{proof}

@@

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\), 
  \(\sigma(n)=\ran{f_n}\)
  for some \(f_n\in\mathbf C(\mc R)\). So let
  \(\tau(R,n)=f_n(R)\) for all \(R\in \mc R\) and \(n<\omega\).
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}=\sigma(n)\),
  \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

@@

>>>>

\begin{abstract}
  Often, selection games have dual games for which a winning
  strategy for a player in one game may be used to create
  a winning strategy 
  For example, the Rothberger selection game involving open covers
  is dual to the point-open game. This extends to a general
  theorem: if \(\{\ran{f}:f\in\mathbf C(\mc R)\}\) is coinitial in \(\mc A\)
  with respect to \(\subseteq\),
  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
  collects the choice functions on the set \(\mc R\),
  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
  are dual selection games. 
\end{abstract}

@@

\begin{definition}
  Write \(X\preceq Y\) if \(X\) is coinitial in \(Y\) with respect to \(\subseteq\);
  that is, \(X\subseteq Y\), and for all \(y\in Y\), there exists \(x\in X\) such that 
  \(x\subseteq y\).
\end{definition}

\begin{definition}
  The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\{\ran f:f\in\mathbf C(\mc R)\}\preceq\mc A.\]
\end{definition}

@@

%\begin{proposition}
%  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
%\end{proposition}
%\begin{proof}
%  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
%  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).
%
%  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
%  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
%  showing \(x\in\bigcup\mc A\).
%\end{proof}

@@

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A\),
  \(\ran{f_n}\subseteq\sigma(n)\)
  for some \(f_n\in\mathbf C(\mc R)\). So let
  \(\tau(R,n)=f_n(R)\) for all \(R\in \mc R\) and \(n<\omega\).
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}\subseteq\sigma(n)\),
  \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\),
  and let \(\tau(n)=\ran{f_n}\in\mc A\). 
  Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

@@

\section{Acknowledgements}

Thanks to Prof. Jared Holshouser for his input during the writing of these results.
